\begin{thebibliography}{99}

\bibitem{Tax2001} Tax D. \textit{One-class classification; Concept-learning in the absence of
counterexamples} // Ph.D thesis. 2001.
\bibitem{Khan2006} Khan S., Madden G. \textit{A Survey of Recent Trends in One Class
Classiffcation} // College of Engineering and Informatics, National University of Ireland Galway.
Ireland. 2006.
\bibitem{Islam2007} Islam R., Chowdhury R. \textit{Spam filtering using ML algorithms} // Universitetets Okonomiske Institute. IADIS International Conference on WWW/Internet. 2007.
%\bibitem{Sun2008} Sun J., Zhang Q., Yuan Z., Huang W., Yan X., Dong J. \textit{Research of Spam Filtering system based on LSA and SHA} // Advances in neural networks. ISNN 2008. 2008.
\bibitem{Sun2008} \textit{Research of Spam Filtering system based on LSA and SHA} / Sun J. [et al.] // Advances in neural networks. ISNN. 2008.
\bibitem{Romanenko2012} Романенко А.\,А. \textit{Категоризация текстов на основе монотонного
классификатора ближайшего соседа} // Выпускная квалификационная работа бакалавра. 2012.
\bibitem{Rijsbergen1979} van Rijsbergen C.\,J. \textit{Information Retrieval} // Butterworth. 2nd ed. 1979.
\bibitem{Groot1974}Де Гроот М. \textit{Оптимальные статистические решения} // М.: Мир, 1974.
\bibitem{Izerman1979} Айзерман М.\,А., Браверман Э.\,М., Розоноэр Л.\,И. \textit{Метод потенциальных функций в теории обучения машин} // М.: Наука, 1970.
\bibitem{Merkov} Мерков А.\,Б. \textit{О статистическом обучении. Лаборатория распознавания образов} // М.: МЦНМО, 2013.
\bibitem{Steinwart}  \textit{An explicit description of the reproducing kernel Hilbert spaces of Gaussian RBF kernels} / Steinwart [et al.] // IEEE Transactions on Information Theory. 2006
\end{thebibliography}
