\begin{thebibliography}{99}
\bibitem{vap99} Vapnik V. \textit{An Overview of Statistical Learning Theory}~// IEEE Transactions on Neural Networks, Vol 10, No. 5, Sept 1999.

\bibitem{tib96} Tibshirani, R. \textit{Regression shrinkage and selection via the lasso}~// Journal of the Royal Statistical Society, Series B, Vol 58, No. 1, pp. 267–288, 1996.

\bibitem{zou05} Zou, H. and T. Hastie. \textit{Regularization and variable selection via the elastic net}~// Journal of the Royal Statistical Society, Series B, Vol. 67, No. 2, pp. 301–320, 2005.

\bibitem{hoerl70} Hoerl, A. E., and R. W. Kennard. \textit{Ridge Regression: Biased Estimation for Nonorthogonal Problems.}~// Technometrics. Vol. 12, No. 1, 1970, pp. 55–67.

\bibitem{dru96} Drucker, Harris; Burges, Christopher J. C.; Kaufman, Linda; Smola, Alexander J.; and Vapnik, Vladimir N. (1997); \textit{Support Vector Regression Machines}, in Advances in Neural Information Processing Systems 9, NIPS 1996, 155–161, MIT Press.

\bibitem{cawley} Gavin C. Cawley and Nicola L. C. Talbot.\textit{Fast Exact Leave-One-Out Cross-Validation of Sparse Least-Squares Support Vector Machines}~// School of Computing Sciences, University of East Anglia, Norwich, United Kingdom.

\bibitem{che14} Chernousova E., Razin N., Krasotkina O., Mottl V., Windridge D. \textit{Linear Regression via Elastic Net: Non-enumerative Leave-One-Out Verification of Feature Selection}~// Springer Optimization and Its Applications 92.

\bibitem{ivch09} Г. И. Ивченко, Ю. И. Медведев \textit{Введение в математическую статитсику}~// ЛКИ, 2009.

\bibitem{voron} Воронцов К. В. \textit{Математические методы обучения по прецедентам}~//2009.

\bibitem{gre12} Гребенников Е. В. \textit{Метод дифференциальной беспереборной кросс-валидации в задачах восстановления зависимостей по эмпирическим данным}~// ВКР бакалавра, МФТИ ФУПМ, ВЦ РАН, 2012.
\end{thebibliography}