\begin{thebibliography}{99}

\bibitem{hoff99} Hofmann T. \textit{Probabilistic latent semantic indexing}~// Proceedings of the 22nd annual international ACM SIGIR conference on Research and development in information retrieval, New York, NY, USA: ACM, 1999, Pp. 50–57.

\bibitem{hoff01} Hofmann T.	\textit{Unsupervised Learning by Probabilistic Latent Semantic Analysis}~// Machine Learning, 2001, Vol.~42, Pp.~177--196.

\bibitem{blei03}  D. M. Blei, A. Y. Ng, and M. I. Jordan. \textit{Latent dirichlet allocation} // Journal of Machine Learning Research, 2003, 3:993–1022

\bibitem{demp77} Dempster A. P., Laird N. M., Rubin D. B. \textit{Maximum likelihood from incomplete data via the EM algorithm}~// Journal of the Royal Statistical Society, Series B, 1977, no. 34, Pp. 1-38.

\bibitem{styv04} Steyvers M., Griffiths T. \textit{Finding scientific topics}~// Proceedings of the National
Academy of Sciences, 2004, Vol. 101, no. Suppl. 1, Pp. 5228–5235.

\bibitem{wang08} Wang Y.  \textit{Distributed Gibbs sampling of latent dirichlet allocation: The gritty
details}, 2008.

\bibitem{ronn89} Ronning G. \textit{Maximum likelihood estimation of dirichlet distributions}~// Journal of Statistical Computation and Simulation, 1989, 32:4, Pp.~215-221.

\bibitem{kull51} Kullback S., Leibler R. A.  \textit{On information and sufficiency}~// The Annals of Mathematical Statistics, 1951, Vol.~22, 1, Pp.~79-86.

\bibitem{asuc09} Asuncion A., Welling M., Smyth P., Teh Y. W. \textit{On smoothing and inference for topic models}~// Proceedings of the International Conference on Uncertainty in Artificial Intelligence, 2009.
\end{thebibliography}